GMSE: an R package for generalised management strategy evaluation

### 2018-04-17 notebook/ms/SI3.Rmd
Work on supporting information

```{r, echo = TRUE}
sim <- gmse(manager_budget = 100000, user_budget = 100000, res_death_K = 93870, 
            manage_target = 70000, RESOURCE_ini = 35000, plotting = FALSE, 
            stakeholders = 80, land_ownership = TRUE, public_land = 0.4, 
            scaring = FALSE, lambda = 0.150, remove_pr = 0.122, time_max = 20, 
            res_death_type = 3, res_consume = 0.01, res_birth_K = 200000, 
            observe_type = 3, agent_view = 1);
```

@@

```{r, eval = TRUE, fig.height = 8}
plot_gmse_results(res = sim$resource, obs = sim$observation, land = sim$land, 
                  agents = sim$agents, paras = sim$paras, ACTION = sim$action, 
                  COST = sim$cost);
```

@@

```{r, eval = TRUE, fig.height = 7, fig.width = 6}
plot_gmse_effort(sim$agents, sim$paras, ACTION = sim$action, COST = sim$cost);
```

```{r, echo = TRUE, fig.height = 8}
sim <- gmse(manager_budget = 10000, user_budget = 10000, res_death_K = 93870, 
            manage_target = 70000, RESOURCE_ini = 63000, plotting = FALSE, 
            stakeholders = 20, land_ownership = TRUE, land_dim_1 = 50, 
            land_dim_2 = 50, public_land = 0.4, scaring = TRUE, lambda = 0.275, 
            remove_pr = 0.122, time_max = 20, res_death_type = 3, ga_seedrep = 0, 
            ga_mingen = 100, res_consume = 0.02);
```

@@

```{r, eval = TRUE, fig.height = 8}
plot_gmse_results(res = sim$resource, obs = sim$observation, land = sim$land, 
                  agents = sim$agents, paras = sim$paras, ACTION = sim$action, 
                  COST = sim$cost);
```

```{r, eval = TRUE, fig.height = 7, fig.width = 6}
plot_gmse_effort(sim$agents, sim$paras, ACTION = sim$action, COST = sim$cost);
```

>>>>

```{r, echo = TRUE}
sim_1 <- gmse(manager_budget = 10000, user_budget = 10000, plotting = FALSE, 
              res_death_K = 93870, manage_target = 70000, RESOURCE_ini = 35000, 
              stakeholders = 80, land_ownership = TRUE, public_land = 0.4, 
              scaring = FALSE, lambda = 0.150, remove_pr = 0.122, time_max = 20, 
              res_death_type = 3, res_consume = 0.01, res_birth_K = 200000, 
              observe_type = 3, agent_view = 1);
```

The results of the above simulation are plotted in Figure SI3-1 below.

```{r, eval = TRUE, fig.height = 8}
plot_gmse_results(res = sim_1$resource, obs = sim_1$observation, 
                  land = sim_1$land, agents = sim_1$agents, paras = sim_1$paras, 
                  ACTION = sim_1$action, COST = sim_1$cost);
```

```{r, eval = TRUE, fig.height = 7, fig.width = 6}
plot_gmse_effort(sim_1$agents, sim_1$paras, ACTION = sim_1$action, 
                 COST = sim_1$cost);
```

```{r, echo = TRUE, fig.height = 8}
sim_2 <- gmse(manager_budget = 10000, user_budget = 10000, plotting = FALSE, 
              res_death_K = 93870, manage_target = 70000, RESOURCE_ini = 35000, 
              stakeholders = 80, land_ownership = TRUE, public_land = 0.4, 
              scaring = TRUE, lambda = 0.150, remove_pr = 0.122, time_max = 20, 
              res_death_type = 3, res_consume = 0.01, res_birth_K = 200000, 
              observe_type = 3, agent_view = 1);
```

@@

```{r, eval = TRUE, fig.height = 8}
plot_gmse_results(res = sim_2$resource, obs = sim_2$observation, 
                  land = sim_2$land, agents = sim_2$agents, paras = sim_2$paras,
                  ACTION = sim_2$action, COST = sim_2$cost);
```

@@

```{r, eval = TRUE, fig.height = 7, fig.width = 6}
plot_gmse_effort(sim_2$agents, sim_2$paras, ACTION = sim_2$action, 
                 COST = sim_2$cost);
```

@@
